A seamless, client-centric programming model for type safe web applications

### 2014-05-02 paper.tex
Update abstract, add Links, Ur/Web and HOP.

\begin{abstract}
We propose a new programming model for web applications which is (1)
seamless; one program and one language is used to produce code for
both client and server, (2) client-centric; the programmer takes the
viewpoint of the client that runs code on the server rather than the
other way around, and (3) functional and type-safe; everything is
implemented as a Haskell library that implicitly takes care of all
networking code. Our aim is to improve the painful and error-prone
experience of today's standard development methods, in which clients
and servers are coded in different languages and communicate with each
other using ad-hoc protocols. We present the design of our library
called Haste.App, an example web application that uses it, and discuss
the implementation and the compiler technology on which it depends.
\end{abstract}

@@

>>>>

\begin{abstract}
We propose a new programming model for web applications which is (1)
seamless; one program and one language is used to produce code for
both client and server, (2) client-centric; the programmer takes the
viewpoint of the client that runs code on the server rather than the
other way around, (3) functional and type-safe; and (4) portable;
everything is implemented as a Haskell library that implicitly takes
care of all networking code. Our aim is to improve the painful and
error-prone experience of today's standard development methods,
in which clients and servers are coded in different languages and
communicate with each other using ad-hoc protocols.
We present the design of our library called Haste.App,
an example web application that uses it, and discuss
the implementation and the compiler technology on which it depends.
\end{abstract}

@@

\paragraph{HOP, Links, Ur/Web and others} In addition to solutions which work
within existing languages, there are several languages specifically created to
target the web domain. These languages tend to target not only the client and
server tiers, but the database tier as well. These languages bring many new,
interesting ideas to the table but suffers from not being compatible with any
more established languages.
